\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement\\Q-aRt Code}

\author{Team \#, Q-aRt QTs
		\\ Elton Schiott schiotek
		\\ Emilio Hajj
		\\ Liam Duncan
}

\date{}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
2016-09-28 & Elton Schiott & Created LaTeX file, and edited text for clarity.\\
2016-12-07 & Liam Duncan & Revision one revisit.\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

\section{Problem Case}
	
	\paragraph{}
	
		The project will focus on redeveloping a python based QR 
		encoder and image interlacer by enhancing and expanding upon certain features of the program. 
		In particular the plan is to improve the scattered and ill-phrased documentation, especially the MIS, as well as to increase
		user friendliness with an improved user interface. The problem being solved
		is a complex mixture between taboo against QR code use in professional graphic
		design for their original aesthetic detriment, a decline in excitement
		about the technology stemming from its innovative stagnation, and an underwhelming
		set of opportunities for creative new applications for the encoding technology.
	
\section{Stakeholders}

	\paragraph{}
	
		The stakeholders for this project are business and marketing firms that 
		wil use QR codes to advertise their products and services. Another 
		group of stakeholders is future developers who will use and modify the 
		application.
	
\section{Use Cases}

	\paragraph{}
	
		The QR code can be utilized as a marketing tool for major companies by 
		attracting users to webpages using artistic and unique Q-aRt generated 
		images. It can also be used by organizations for fundraising and 
		awareness purposes. It is a unique way to promote a business, product, 
		or event. Unlike traditional codes, this program allows designers of
		graphics for groups to save space on their graphics for other information 
		by combining QR code images and other components such as logos, or even 
		containing the entire graphical message within the bounds of the code,
		and utitlize QR encoding technology in creative ways to catch the attention
		of their desired audience.

\end{document}